Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-05 testbed.tex

@@

\item Clone the Kodo repository in the server by executing: \\
\texttt{git clone git://github.com/steinwurf/kodo.git} in \texttt{\$HOME}.
\textbf{Change the repo to kodo-rlnc or kodo-cpp since just raw kodo is going
to be depreceated soon} \\

>>>>

WRITE SOMETHING ABOUT THIS AND MENTION HOW TO REQUEST A KODO LICENSE

@@

\item Create a directory to hold our code:
\begin{lstlisting}[]
$ CODEDIR="${HOME}/code"
$ mkdir -p ${CODEDIR}
$ cd ${CODEDIR}
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\item Clone the Kodo repository and change directory into the repository: \\
\begin{lstlisting}[]
$ git clone https://github.com/steinwurf/kodo-cpp.git
$ cd kodo-cpp
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\item Configure Kodo to build executables for the \ac{ARM} architecture using our toolchain:
\begin{lstlisting}[]
$ python waf configure --cxx_mkspec=cxx_raspberry_gxx49_arm
...
'configure' finished successfully (0.620s)
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\item Build executables:
\begin{lstlisting}[]
$ python waf build
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}
